### 2013-10-04 Tex/chapters/results.tex
Daten mit den Werten der neuen Bootstrap Methode aktualisiert
es hat sich relativ wenig getan, vorherige Beschreibung passt immer
noch so gut, wie vorher
markierung von T_c hinzugefügt
Erscheinungsbild der Tabellen konsistenter
alle Werte gleiche Anzahl an Nachkommastellen
Rechtschreibfehler und so

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also Sec.\ \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l r r r r r}
            \toprule
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \midrule
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
            \bottomrule
        \end{tabular}
        \caption[Autocorrelation Times $\tau$ and Equilibration Times
            $t_{eq}$ for Different System Sizes $L$]{
            Autocorrelation times $\tau$ and equilibration times
            $t_{eq}$ for different system sizes $L$. All values are generously
            rounded up and determined as the maximum over all \(\sigma\) and \(T\).
        }
        \label{tab:tauAndTeq}
    \end{table}\\
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity so
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
    \cite{Bootstrap}.
    There are two kinds of errors in this simulations. On the one hand
    there are thermal fluctuations in the simulation of one graph realization and
    on the other hand there are fluctuations in the structure of the realizations.
    To account for both, first a resampling of the "timeline" of one
    realization is performed. From these resamples the expected values of
    the observables \(\avg{\abs{m}}, \chi\) and \(g\) are estimated for each
    realization. Those are then resampled and from the resampled values
    one bootstrap average \(\avg{O}_b\) is calculated. This procedure is
    repeated until 20 different bootstrap averages are present. Their
    mean and standard deviation are used as \(\overline{\avg{O}}\) and
    its standard error \(\Delta \overline{\avg{O}}\).
    For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot divded by root of the chi-squared per degree of freedom
    as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
    source plotting program used for all plots and fits in this thesis.
    Also note that dotted lines in the plots are -- if not noted otherwise --
    cubic spline interpolations purely meant to be guides to the eye.

\subsection{Short Analysis of the Autocorrelation Time}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) according to Eq.\ \ref{eq:tau} is given to
    illustrate the benefits of the used Wolff cluster algorithm.\\
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note that these are the unrounded values
    of Tab.\ \ref{tab:tauAndTeq}.
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
                double logarithmic axis with a power law fit \(\tau \propto L^z\) (dotted line)
                to determine the dynamical exponent \(z'\).
                (Errorbars are the standard error estimated by bootstrap resampling.)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
    spin in every step, thus the autocorrelation time is one sweep.
    (Note that this is not the only explanation for the small values of \(\tau\).
    The parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.)
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    But it is also possible that these are again finite size effects.
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    Sec.\ \ref{sssec:eqtime}.
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    expected for the Wolff cluster algorithm at \(T_c\). On the one hand the number of sweeps,
    in which \(\tau\) is measured in this thesis, are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting that it obeys a power law
    \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more detailed inspection, one
    would perform the simulation at the critical point, which will be
    determined subsequently.

\subsection{Finite-Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \begin{equation}
        \chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}
    \end{equation}
    will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L} Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$. The position of the slope,
            and hence the critical temperature, moves to lower temperatures
            with increasing \(\sigma\) (\(0.0 \le \sigma \le 1.2\))
            \subref{sfig:smeared_out:meanM} Effects of different system
            sizes at \(\sigma = 0\), i.e.\ the square lattice Ising ferromagnet.
            The \(L=16\) curve is much less steep than the \(L=128\) curve.
            Note that the \(L=\infty\) curve has not an infinite slope but
            follows a power law function near \(T_c\).
        }
        \label{fig:smeared_out}
    \end{figure}\\
    As evident from the figure there occurs no steep decline to zero, but a
    smooth one. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finite-size effects}.
    These finite-size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as shown
    in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly, the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling (FSS)
    methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
    exponents. Such a FSS analysis will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in Sec.\ \ref{ssec:binderIntersections}.

@@

    because \(c\) diverges logarithmically and not exponentially.

@@

    The same principle can be used to determine the other two exponents.

@@

    Also the collapse of the binder cumulant, as mentioned before and shown

@@

                of an Ising model on an RNG at \(\sigma=1\).

@@

                of an Ising model on an GG at \(\sigma=1\).

@@

            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\

@@

            GG           & 0.0 & 2.2687(5)& 0.998(8) & 1.735(2) & 0.1262(4)\\
                         & 0.1 & 2.895(4) & 0.999(19)& 1.744(5) & 0.133(6) \\
                         & 0.3 & 2.527(1) & 1.029(30)& 1.724(16)& 0.129(12)\\
                         & 0.5 & 2.238(1) & 1.006(5) & 1.750(12)& 0.125(13)\\
                         & 1.0 & 2.128(2) & 1.038(32)& 1.743(17)& 0.123(16)\\

@@

    yield meaningful results.

@@

@@

        \begin{tabular}{l l l l l}

@@

             & \multicolumn{2}{c}{RNG} & \multicolumn{2}{c}{GG}\\
            \cmidrule(rl){2-3} \cmidrule(rl){4-5}
            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)}\\

@@

            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5)\\
            0.03 & 2.2679(4)&          & 2.851(1) &         \\
            0.05 & 2.2662(5)&          & 2.863(1) &         \\
            0.08 & 2.2548(6)&          & 2.882(2) &         \\
            0.10 & 2.205(1) & 2.2058(8)& 2.893(2) & 2.895(4)\\
            0.12 & 2.1010(5)&          & 2.903(3) &         \\
            0.15 & 1.898(2) &          & 2.903(3) &         \\
            0.20 & 1.624(1) & 1.627(2) & 2.8274(6)&         \\
            0.25 & 1.4812(5)&          & 2.676(2) &         \\
            0.30 & 1.407(2) &          & 2.526(4) & 2.527(1)\\
            0.40 & 1.327(4) &          & 2.332(4) &         \\
            0.50 & 1.2818(2)& 1.2825(7)& 2.233(7) & 2.238(1)\\
            0.60 & 1.252(2) &          & 2.183(3) &         \\
            0.70 & 1.234(1) &          & 2.154(8) &         \\
            0.80 & 1.223(1) &          & 2.140(3) &         \\
            0.90 & 1.214(4) &          & 2.132(1) &         \\
            1.00 & 1.208(5) & 1.2123(3)& 2.121(8) & 2.128(2)\\
            1.10 & 1.206(1) &          & 2.116(11)&         \\
            1.20 & 1.204(2) &          & 2.113(4) &         \\

@@

            values of \(T_c\) which were determined before via finte
            size scaling analysis. The other values are determined by
            the intersection of the binder cumulants \(g\) for different
            system sizes. The values of both methods match.

@@

    through the intersection of the binder cumulant are always in good

@@

    \subsubsection{Influence of the Average Degree on the Critical Temperature}
        One basic property of a graph is its average \emph{degree} \(K\) -- sometimes
        called average \emph{coordination number}. \(K\) is defined as the mean count
        of neighbors per node.
            K = \frac{2}{N} \# E.
            \label{eq:degree}
        Where \(\# E\) is the number of edges of the graph.
        For a Poisson point process, i.e.\ for \(\sigma \gtrsim 1\),
        the average degree of the mentioned graph types are known.
        \(K_{DT} = 6\) \cite{DelaunayDegree}, \(K_{GG} = 4\) \cite{notPChristoph} and \(K_{RNG} = 2.5576(3)\) \cite{RNGCell}.
        Indeed, for \(\sigma \gtrsim 1\) Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:GG}\subref{sfig:deg:RNG}
        confirm the last two values.\\
        It is well known that the degree has an impact on the critical temperature.
        For example the Honeycomb lattice is of degree \(K=3\) and the
        respective critical temperature can be obtained by analytic means \cite{Wannier1945},
        yielding
            \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52.
            \label{eq:exactHCTc}
        Note that this is lower than the critical temperature \(T_c = 2.269...\)
        characteristic for the square lattice with degree \(K=4\).\\
        This is plausible, because more edges lead to more neighbors.
        Consider, e.g.\ a fully polarized spin configuration, e.g.\ all
        spins are pointing up. Now, the energy needed to flip a spin so
        that it assumes an orientation opposite to the orientation of its
        neighbors increases with the number of its neighbors. So the more edges are in
        the graph the more stable the system becomes with respect to spin flips
        at low \(T\), leading to an increasing value of \(T_c\).
        This is also an explanation why the \(T_c\) of the RNG is always
        lower than that of the GG: The degree of the RNG is lower.\\
        If one plots the degree of the graphs at different \(\sigma\) like
        in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
        one recognizes that \(T_c\) and \(K\) are evidently correlated.
        The values for \(K\) are obtained as an average over \(100\)
        realizations of each graph type for \(L=16\) and \(L=32\) lattices.
        %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
        %~ In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        %~ one can see that these curves are almost identical and the small
        %~ errorbars suggest that they are sufficiently precise for this purpose.

>>>>

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also Sec.\ \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l r r r r r}
            \toprule
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \midrule
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
            \bottomrule
        \end{tabular}
        \caption[Autocorrelation Times $\tau$ and Equilibration Times
            $t_{eq}$ for Different System Sizes $L$]{
            Autocorrelation times $\tau$ and equilibration times
            $t_{eq}$ for different system sizes $L$. All values are generously
            rounded up and determined as the maximum over all \(\sigma\) and \(T\).
        }
        \label{tab:tauAndTeq}
    \end{table}\\
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity so
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
    \cite{Bootstrap}.
    There are two kinds of errors in this simulations. On the one hand
    there are thermal fluctuations in the simulation of one graph realization and
    on the other hand there are fluctuations in the structure of the realizations.
    To account for both, first a resampling of the "timeline" of one
    realization is performed. From these resamples the expected values of
    the observables \(\avg{\abs{m}}, \chi\) and \(g\) are estimated for each
    realization. Those are then resampled and from the resampled values
    one bootstrap average \(\avg{O}_b\) is calculated. This procedure is
    repeated until 20 different bootstrap averages are present. Their
    mean and standard deviation are used as \(\overline{\avg{O}}\) and
    its standard error \(\Delta \overline{\avg{O}}\).
    For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot divded by the root of the chi-squared per degree of freedom
    as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
    source plotting program used for all plots and fits in this thesis.
    Also note that dotted lines in the plots are -- if not noted otherwise --
    cubic spline interpolations purely meant to be guides to the eye.

\subsection{Short Analysis of the Autocorrelation Time}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) according to Eq.\ \ref{eq:tau} is given to
    illustrate the benefits of the used Wolff cluster algorithm.\\
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note that these are the unrounded values
    of Tab.\ \ref{tab:tauAndTeq}.
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
                double logarithmic axis with a power law fit \(\tau \propto L^{z'}\) (dotted line)
                to determine the dynamical exponent \(z'\).
                (Errorbars are the standard error estimated by bootstrap resampling.)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
    spin in every step, thus the autocorrelation time is one sweep.
    (Note that this is not the only explanation for the small values of \(\tau\).
    The parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.)
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    But it is also possible that these are again finite size effects.
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    Sec.\ \ref{sssec:eqtime}.
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    expected for the Wolff cluster algorithm at \(T_c\). On the one hand the number of sweeps,
    in which \(\tau\) is measured in this thesis, are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting that it obeys a power law
    \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more detailed inspection one
    would perform the simulation at the critical point which will be
    determined subsequently.

\subsection{Finite-Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \begin{equation}
        \chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}
    \end{equation}
    will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L} Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$. The position of the slope,
            and hence the critical temperature, moves to lower temperatures
            with increasing \(\sigma\) (\(0.0 \le \sigma \le 1.2\))
            \subref{sfig:smeared_out:meanM} Effects of different system
            sizes at \(\sigma = 0\), i.e.\ the square lattice Ising ferromagnet.
            The \(L=16\) curve is much less steep than the \(L=128\) curve.
            Note that the \(L=\infty\) curve follows a power law function near \(T_c\).
        }
        \label{fig:smeared_out}
    \end{figure}\\
    As evident from the figure there occurs no steep decline to zero, but a
    smooth one. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finite-size effects}.
    These finite-size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as shown
    in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly, the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling (FSS)
    methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
    exponents. Such a FSS analysis will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in Sec.\ \ref{ssec:binderIntersections}.

@@

    because \(c\) diverges logarithmically and not following a power law.

@@

@@

    Also the collapse of the Binder cumulant, as mentioned before and shown

@@

                of an Ising model on RNG at \(\sigma=1\).

@@

                of an Ising model on GG at \(\sigma=1\).

@@

            RNG          & 0.0 & 2.2688(7) & 0.997(11)& 1.737(3) & 0.131(1) \\
                         & 0.1 & 2.2053(6) & 0.994(10)& 1.745(5) & 0.128(3) \\
                         & 0.2 & 1.6265(19)& 1.017(16)& 1.758(14)& 0.157(12)\\
                         & 0.5 & 1.2825(9) & 1.011(18)& 1.746(16)& 0.146(13)\\
                         & 1.0 & 1.2125(5) & 1.010(2) & 1.764(14)& 0.133(12)\\

@@

            GG           & 0.0 & 2.2688(6) & 0.999(13)& 1.739(3) & 0.128(1)\\
                         & 0.1 & 2.8944(43)& 1.001(12)& 1.745(6) & 0.135(6) \\
                         & 0.3 & 2.5281(27)& 1.034(29)& 1.718(15)& 0.118(11)\\
                         & 0.5 & 2.2388(9) & 1.006(5) & 1.747(12)& 0.125(11)\\
                         & 1.0 & 2.1275(20)& 1.036(31)& 1.750(16)& 0.125(15)\\

@@

    yield meaningful results. An even better method would be the
    \emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
    But the simple cubic spline interpolation seems to deliver results
    that are good enough, because the temperatures of the measurements are
    sufficiently near to each other. Also cubic spline interpolation is
    far easier to obtain.

@@

            The vertical line marks the known critical temperature for the
            square lattice Ising model \(T_{c} = 2.2691...\).

@@

        \begin{tabular}{l l@{}l l@{}l l@{}l l@{}l}

@@

             & \multicolumn{4}{c}{RNG} & \multicolumn{4}{c}{GG}\\
            \cmidrule(rl){2-5} \cmidrule(rl){6-9}
            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{2}{c}{\(T_c\)} & \multicolumn{2}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{2}{c}{\(T_c\)} & \multicolumn{2}{c}{\(T_c^{\mathrm{collapse}}\)}\\

@@

            0.00 & 2.2689& (2)& 2.2688&(7) & 2.2689& (2) & 2.2688&(6) \\
            0.03 & 2.2679& (3)&       &    & 2.8510& (7) &       &    \\
            0.05 & 2.2661& (5)&       &    & 2.8629&(10) &       &    \\
            0.08 & 2.2548& (5)&       &    & 2.8824&(17) &       &    \\
            0.10 & 2.2049& (9)& 2.2053&(6) & 2.8933&(22) & 2.8944&(43)\\
            0.12 & 2.1012& (4)&       &    & 2.9034&(20) &       &    \\
            0.15 & 1.8980&(21)&       &    & 2.9036&(21) &       &    \\
            0.20 & 1.6239&(21)& 1.6265&(19)& 2.8272&(12) &       &    \\
            0.25 & 1.4816& (7)&       &    & 2.6760&(21) &       &    \\
            0.30 & 1.4071&(20)&       &    & 2.5260&(51) & 2.5281&(27)\\
            0.40 & 1.3267&(28)&       &    & 2.3317&(44) &       &    \\
            0.50 & 1.2817& (2)& 1.2825&(9) & 2.2322&(83) & 2.2388&(9) \\
            0.60 & 1.2519&(16)&       &    & 2.1841&(26) &       &    \\
            0.70 & 1.2337&(14)&       &    & 2.1540&(79) &       &    \\
            0.80 & 1.2224&(16)&       &    & 2.1410&(19) &       &    \\
            0.90 & 1.2142&(35)&       &    & 2.1320& (5) &       &    \\
            1.00 & 1.2083&(48)& 1.2125&(5) & 2.1208&(82) & 2.1275&(20)\\
            1.10 & 1.2055&(15)&       &    & 2.1164&(85) &       &    \\
            1.20 & 1.2034&(12)&       &    & 2.1133&(45) &       &    \\

@@

            values of \(T_c\) which were determined before via finte-size
            scaling analysis. The other values are determined by
            the intersections of the Binder cumulants \(g\) for different
            the intersections of the Binder cumulants \(g\) for different
            system sizes. The values of both methods match within errorbars.

@@

    through the intersections of the Binder cumulants are always in good

@@

    \subsubsection{Influence of the Average Degree on the Critical Temperature}
        One basic property of a graph is its average \emph{degree} \(K\) -- sometimes
        called average \emph{coordination number}. \(K\) is defined as the mean count
        of neighbors per node.
        \begin{equation}
            K = \frac{2}{N} \# E.
            \label{eq:degree}
        \end{equation}
        Where \(\# E\) is the number of edges of the graph.
        For a Poisson point process, i.e.\ for \(\sigma \gtrsim 1\),
        the average degree of the mentioned graph types are known.
        \(K_{DT} = 6\) \cite{DelaunayDegree}, \(K_{GG} = 4\) \cite{notPChristoph} and \(K_{RNG} = 2.5576(3)\) \cite{RNGCell}.
        Indeed, for \(\sigma \gtrsim 1\) Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:GG}\subref{sfig:deg:RNG}
        confirm the last two values.\\
        It is well known that the degree has an impact on the critical temperature.
        For example the Honeycomb lattice is of degree \(K=3\) and the
        respective critical temperature can be obtained by analytic means \cite{Wannier1945},
        yielding
        \begin{equation}
            \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52.
            \label{eq:exactHCTc}
        \end{equation}
        Note that this is lower than the critical temperature \(T_c = 2.269...\)
        characteristic for the square lattice with degree \(K=4\).\\
        This is plausible, because more edges lead to more neighbors.
        Consider, e.g.\ a fully polarized spin configuration, e.g.\ all
        spins are pointing up. Now, the energy needed to flip a spin so
        that it assumes an orientation opposite to the orientation of its
        neighbors increases with the number of its neighbors. So the more edges are in
        the graph the more stable the system becomes with respect to spin flips
        at low \(T\), leading to an increasing value of \(T_c\).
        This is also an explanation why the \(T_c\) of the RNG is always
        lower than that of the GG: The degree of the RNG is lower.\\
        If one plots the degree of the graphs at different \(\sigma\) like
        in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
        one recognizes that \(T_c\) and \(K\) are evidently correlated.
        The values for \(K\) are obtained as an average over \(100\)
        realizations of each graph type for \(L=16\) and \(L=32\) lattices.
        %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
        %~ In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        %~ one can see that these curves are almost identical and the small
        %~ errorbars suggest that they are sufficiently precise for this purpose.
        It seems reasonable to normalize \(T_c\) by the degree of the underlying
        graph. This is done in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
        Indeed the normalization eliminates the jump and reduces the
        slope of the \(T_c\) curve for the GG. Hence it reduces differences
        between the RNG and the GG. However the elimination of the jump is
        unfortunately a coincidence and probably caused by a lucky choice of the
        function, which determines the local coupling constants \(J_{ij}\). As proof for
        this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis
        is performed for a model with fixed \(J\). There the jump gets narrower
        but is still existent.\\
        \begin{figure}[htbp]
            \centering
            \subfigure[][]
            {
                \label{sfig:deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
            }
            \subfigure[][]
            {
                \label{sfig:deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_deg}
            }

            \caption[Critical Temperature Normalized by Degree of the Graph]
                Top: Degree \(K\) of graph over different
